%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Doctorate Degree in Electrical Engineering - Research Line: Computing and Robotics} % 
    {Federal University of Bahia - UFBA} % Institution
    {Salvador, BA} % Location
    {Fev. 2023 - Mar. 2027} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Development triggered event algorithm based on FPGA for the ATLAS experiment at the Large Hadron Collider (LHC-CERN).}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Master's Degree in Electrical Engineering - Research Line: Computing and Robotics} % 
    {} % Institution
    {} % Location
    {Apr. 2018 - Dec. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Communication between \textit{Robot Operating System - ROS} and \textit{System-on-a-chip - SoC} with integrated FPGA.}
        % \item {Scholarship from Higher Education Personal Improvement Coordination - CAPES }
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Specialization in Biomedical Engineering} % 
    {Estácio de Sá University} % Institution
    {Salvador, BA} % Location
    {Oct. 2017 - Feb. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Convolutional Neural Network for Detection of QRS Complexes in Electrocardiogram Signals}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Bachelor's degree in Electronic Engineering} % Degree
    {Faculty of Science and Technology - ÁREA1} % Institution
    {Salvador, BA} % Location
    {Feb. 2008 - Jul. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Command prototype to fit X-ray equipment to the standards required by the National Health Surveillance Agency - ANVISA.}
        \item {Undergraduate research scholarship for two years}
      \end{cvitems}
    }

\end{cventries}
