%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects and Research}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Flatfish - Sipem} % Affiliation/role
{SENAI CIMATEC} % Organization/group
{Salvador, BA} % Location
{Oct. 2023 - currently} % Date(s)
{
  \begin{cvitems} % Description(s) of experience/contributions/knowledge
    \item {Mobile underwater robotics development project.}
    \item {Development in C/C++ language.}
    \item {Tools: Gitlab, Docker, Hyro.}
    % \item {Electronic and mechanical project development.}
  \end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {SuBot - CTG Brasil (China Three Gorges Corporation)} % Affiliation/role
    {} % Organization/group
    {} % Location
    {Oct. 2021 - Sep. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Mobile robotics development project for inspection of high voltage substations.}
        \item {Development of ROS nodes in C/C++ and Python language.}
        \item {Hardware and firmware development for actuator systems and peripheral communication.}
        \item {Electronic and mechanical project development.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {DIGISUB - Petrobras} % Affiliation/role
    {} % Organization/group
    {} % Location
    {Apr. 2019 - Oct. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {3D digitizer development project of underwater surfaces in deep water.}
        \item {Development of ROS nodes in C/C++ and Python language.}
        \item {Hardware and firmware development for actuator systems and peripheral communication.}
        \item {Prototype power system sizing: sources, AC-DC/DC-DC converters, batteries.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Master's project} % Affiliation/role
    {Polytechnic School of the Federal University of Bahia - UFBA} % Organization/group
    {Salvador, BA} % Location
    {Dec. 2018 - Dec. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {1 GigE communication development between FPGA and ROS.}
        \item {Hardware project in verilog for implementation in SOC/FPGA (Cyclone V - Intel).}
        \item {Socket programming in C/C++ language for linux.}
        \item {Development of ROS nodes in C/C++ language.}
        \item {Paper presented at \underline{\href{https://ieee-lascas.org/}{\emph{IBERCHIP 2022}}}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate research scholarship} % Affiliation/role
    {Faculty of Science and Technology - ÁREA1} % Organization/group
    {Salvador, BA} % Location
    {Jul. 2011 - Jul. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Development of a microcontrolled command to fit old X-ray equipment to current technical standards.}
        \item {Programming 8051 family microcontrollers in assembly language.}
        \item {Research of the technical standards established by ANVISA in relation to X-ray equipment.}
        \item {Presentation of monthly reports with activities developed in the period.}
        \item {Publication of the results in an article in the journal \underline{\href{https://cientefico.emnuvens.com.br/cientefico/article/view/58}{\emph{Cientefico ISSN 1677-1591, jul/dez 2013}}}.}
      \end{cvitems}
    }
    

%---------------------------------------------------------
\end{cventries}

